Variational Monte Carlo on bosonic systems

### 2018-03-21 project_1/article/article.tex
Add correct energies
Add run time for large system

    \begin{table}
        \centering
        \caption{One particle in one dimension for the analytic expression with
        $2^{21}$ Monte Carlo cycles and step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$ & $A$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56661&0.00026&0.00133&0.89121&0.39765\\
                0.34&0.53858&0.00019&0.00096&0.88419&0.34550\\
                0.38&0.51822&0.00013&0.00062&0.87823&0.34849\\
                0.42&0.50770&0.00009&0.00037&0.87136&0.36115\\
                0.46&0.50197&0.00004&0.00018&0.86589&0.34705\\
                0.50&0.50000&0.00000&0.00000&0.86092&0.35124\\
                0.54&0.50146&0.00004&0.00016&0.85497&0.34875\\
                0.58&0.50592&0.00007&0.00029&0.84999&0.34705\\
                0.62&0.51180&0.00011&0.00041&0.84455&0.34861\\
                0.66&0.51983&0.00014&0.00051&0.84014&0.36164\\
                0.70&0.52742&0.00017&0.00063&0.83516&0.35525\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_analytic}
    \end{table}

    \begin{table}
        \centering
        \caption{One particle in one dimension for the numeric expression with
        $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56494&0.00026&0.00131&0.89160&0.35031\\
                0.34&0.53933&0.00020&0.00097&0.88427&0.37179\\
                0.38&0.51841&0.00014&0.00063&0.87840&0.34806\\
                0.42&0.50737&0.00008&0.00037&0.87182&0.34957\\
                0.46&0.50211&0.00004&0.00018&0.86549&0.34976\\
                0.50&0.50000&0.00000&0.00000&0.86041&0.34791\\
                0.54&0.50136&0.00004&0.00015&0.85532&0.34858\\
                0.58&0.50525&0.00007&0.00028&0.84945&0.34703\\
                0.62&0.51181&0.00011&0.00040&0.84535&0.34517\\
                0.66&0.52002&0.00014&0.00051&0.84053&0.34858\\
                0.70&0.52778&0.00017&0.00061&0.83560&0.34818\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_numeric}
    \end{table}

    \begin{table}
        \centering
        \caption{BLEH}
        \begin{ruledtabular}
            \begin{tabular}{c|ccc|ccc}
                & \multicolumn{3}{c|}{Analytic}
                & \multicolumn{3}{c}{Numeric} \\
                \hline
                $N$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                1  \\
                10 \\
                100 \\
                500
            \end{tabular}
        \end{ruledtabular}
        \label{tab:initial_optimum_comparison}
    \end{table}

	\begin{table*}[ht]
		\centering
		\caption{Brute force Metropolis-Hasting at optimum value $\alpha = \frac{1}{2}$ in three dimensions. Step length = 0.1.}
		\begin{tabular}{c|ccc|ccc}
			  & \multicolumn{3}{c|}{Analytic} & \multicolumn{3}{c}{Numeric} \\ \hline
			No. of particles & E($\alpha$) & $\sigma^2$(E) & CPU time [s] & E($\alpha$) & $\sigma^2$(E) & CPU time [s] \\ \hline
			1					 	&   1.5000		  & 0.0000			&  0.42562		& 1.29538		 & 0.10489		   & 0.69979  \\
			10						&  15.0000	  & 0.0000			&  0.78426 		& 7.70527		 & 3.91873		   & 7.06599	 \\
			100					&  150.0000	  & 0.0000			&  4.34369		& 74.22956 	 & 29.77369		   & 481.69100 \\
			500					&	750.0000	  & 0.0000			&  21.32269		& 362.01744	 & 51.52385         & 28409.41744\\ \hline
		\end{tabular}
	\end{table*}

>>>>

    \begin{table}
        \centering
        \caption{One particle in one dimension for the analytic expression with
        $2^{21}$ Monte Carlo cycles and step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$ & $A$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56244&0.00026&0.00129&0.89185&0.43238\\
                0.34&0.53652&0.00019&0.00094&0.88465&0.38340\\
                0.38&0.51863&0.00013&0.00063&0.87844&0.37200\\
                0.42&0.50805&0.00009&0.00038&0.87161&0.37978\\
                0.46&0.50201&0.00004&0.00017&0.86594&0.37214\\
                0.50&0.50000&0.00000&0.00000&0.86047&0.37162\\
                0.54&0.50183&0.00004&0.00015&0.85543&0.37959\\
                0.58&0.50566&0.00007&0.00029&0.84994&0.37778\\
                0.62&0.51175&0.00011&0.00041&0.84479&0.37368\\
                0.66&0.51906&0.00014&0.00052&0.84000&0.37257\\
                0.70&0.52883&0.00017&0.00062&0.83570&0.37342\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_analytic}
    \end{table}

    \begin{table}
        \centering
        \caption{One particle in one dimension for the numeric expression with
        $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30000&0.56675&0.00026&0.00135&0.89098&0.52634\\
                0.34000&0.53714&0.00019&0.00096&0.88479&0.52186\\
                0.38000&0.51836&0.00013&0.00062&0.87820&0.52351\\
                0.42000&0.50717&0.00009&0.00038&0.87180&0.52892\\
                0.46000&0.50184&0.00004&0.00017&0.86581&0.51759\\
                0.50000&0.50000&0.00001&0.00001&0.86024&0.52427\\
                0.54000&0.50133&0.00004&0.00015&0.85520&0.52052\\
                0.58000&0.50520&0.00007&0.00028&0.84971&0.52156\\
                0.62000&0.51120&0.00011&0.00039&0.84481&0.51830\\
                0.66000&0.51896&0.00014&0.00052&0.83990&0.51865\\
                0.70000&0.52794&0.00017&0.00061&0.83506&0.51255\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_numeric}
    \end{table}

    \begin{table}
        \caption{Comparison of energy, standard deviation and the CPU time for
        $\alpha = 0.5$ (the correct minimum) for the analytic and numeric
        schemes in three dimensions and $N$ particles. The step length is
        $0.5$.}
        \centering
        \begin{ruledtabular}
            \begin{tabular}{r|rrr|rrr}
                & \multicolumn{3}{c|}{Analytic}
                & \multicolumn{3}{c}{Numeric} \\
                \hline
                $N$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$
                & $\langle E_L\rangle$ & $\sigma_b$
                & $t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                1 & 1.5 & 0.0 & 0.50
                & 1.49997 & 0.00008 & 0.73 \\
                10 & 15.0 & 0.0 & 0.73
                & 14.98278 & 0.00867 & 6.40 \\
                100 & 150.0 & 0.0 & 4.13
                & 149.81453 & 0.81501 & 387.60 \\
                500 & 750.0 & 0.0 & 19.16
                & 773.85435 & 20.69789 & 9595.02
            \end{tabular}
        \end{ruledtabular}
        \label{tab:initial_optimum_comparison}
    \end{table}
